---
title: "Avg. Distance of US Capitals from Each Other"
author: "Faisal Hoda"
date: "July 20, 2017"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

#### This presentation is a deliverable required for 'Developing Data Products' Course week 4 project on coursera.
7/20/2017

- The application was built using Shiny: https://fhoda.shinyapps.io/wk4_project/

- Source code is on GitHub: https://github.com/fhoda/dp_project_capitaldistance
  * `app.R` contains both server and ui code.

## About the App
The application presents the average distance of capital cities from each other.

- Average distance for each capital from all other capitals was computed in `avg_dist_calculator.R`. 
- Then the shiny library was used to plot a histogram on the resulting data.
- The app allows users to change the bin size dynamically from 1-50.

## Data
```{r cars, echo = TRUE}
capitals = read.csv("capitals.csv", header = TRUE)

head(capitals)
```

## Histogram
```{r pressure}
x    <- capitals$avg_distance
hist(x, col = 'darkgray', border = 'white', 
           xlab = "Avg. Distances", 
           main = "Histogram of Avg. Distances of US Capital Cities from each other"
           )
```

